Revision Plan for SIGCOMM'24 Paper \#293

### 2024-05-21 revision_plan.tex
A5

\noindent\textcolor{blue}{\textbf{Response A.5}
}

>>>>

\noindent\textcolor{blue}{\textbf{Response A.5}
PPT actually will not send the opportunity packet when 10 more flows arrive.
Specifically, traffic bursts result in more ECN-marked packets.
The value of $\alpha$ increases due to Eq. (1), when PPT will not send any opportunity packets.
}

\textcolor{blue}{We have already run a simulation and shown when there are multiple concurrent flows, DCTCP may cut windows simultaneously, thus causing a sudden drain on the switch buffer and leaving bandwidth underutilized. Please see Fig.1 for more details.}

\textcolor{blue}{DCTCP leaves significant spare bandwidth as it ramps up to the maximum window. So, PPT fills the spare bandwidth by sending low-priority opportunity packets. Even if the link is fully utilized, it can be rapidly backtracked to DCTCP by dropping low-priority opportunity packets.}
